Sexual selection, environmental variation, range size and speciation in passerine

### 2018-10-10 Manuscript.Rmd
Fix CV for BAMM

---
title: Sexual selection, environmental variation, range size and speciation in passerine
  birds
author:
- Justin G. Cally*\textsuperscript{§}, Devi Stuart-Fox\textsuperscript{§}, Luke Holman\textsuperscript{§} and Iliana Medina Guzmán\textsuperscript{§}
- ~
- '*\textit{justin.g.cally@gmail.com}'
bibliography: References/SS_Extinction.bib
output:
  word_document:
    pandoc_args: --smart
  html_document: default
  pdf_document: default
header-includes: \usepackage{microtype} \usepackage[all]{hypcap} \usepackage{amsmath}
  \usepackage{booktabs} \usepackage{caption} \usepackage[labelfont=bf]{caption} \usepackage{titling}
  \pretitle{\begin{flushleft}\LARGE} \posttitle{\par\end{flushleft}\vskip 0.5em} \preauthor{\begin{flushleft}\large
  \lineskip 0.5em} \postauthor{\par\end{flushleft}} \predate{\begin{flushleft}\large}
  \postdate{\par\end{flushleft}} \usepackage{fancyhdr} \pagestyle{fancy} \fancyhead[LO,LE]{\textsl{\leftmark}}
  \rhead[]{Sexual Selection and Speciation} \usepackage[noabbrev,capitalise]{cleveref}
  \usepackage{titlefoot} \usepackage{amssymb} \usepackage{rotating} \usepackage{lineno}
  \linenumbers \usepackage{setspace}\onehalfspacing \usepackage[font={small}]{caption}
  \usepackage{epigraph} \setlength\epigraphwidth{5.25in} \setlength\epigraphrule{0pt}
  \setlength\beforeepigraphskip{1\baselineskip} \setlength\afterepigraphskip{2\baselineskip}
  \renewcommand*{\textflush}{flushright} \renewcommand*{\epigraphsize}{\footnotesize\itshape}
  \usepackage{hyperref}\hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue}
  \raggedbottom
csl: References/AmNat.csl
abstract: 'Sexual selection may influence patterns of diversification; yet controversy remains on whether sexual selection leads to a net increase or decrease in speciation rate, or even elevates extinction. Sexual selection is predicted to increase speciation rate as it can facilitate adaptation to new environments, and work alongside divergent natural selection to swiftly promote reproductive isolation. However, sexual selection frequently favours investment in costly or harmful traits that may reduce adaptation and affect diversification. Here, we investigate the association of sexual selection with speciation and extinction in passerine birds. We use two measures of sexual selection: sexual dichromatism (n = 5,812 species) and a multivariate measure of male-biased sexual selection (sexual dimorphism, polygyny and paternal care; n = 2,465), three distinct measures of speciation ($\lambda_{DR}$, $\lambda_{ND}$, $\lambda_{BAMM}$) and one measure of extinction ($\mu_{BAMM}$). Importantly, we test whether the effects of sexual selection on speciation are dependent upon ecological pressures such as temperature variability across time and space, primary productivity and range size. We find that male-biased sexual selection but not sexual dichromatism predicts speciation. Additionally, we find that birds with smaller ranges have higher speciation rates; although the direction of causality is unclear.'
---
\maketitle\unmarkedfntext{\textsuperscript{§}School of BioSciences, The University of Melbourne, Victoria, Australia.}

>>>>

---
title: Sexual selection, environmental variation, range size and speciation in passerine
  birds
author:
- Justin G. Cally*\textsuperscript{§}, Devi Stuart-Fox\textsuperscript{§}, Luke Holman\textsuperscript{§} and Iliana Medina Guzmán\textsuperscript{§}
- ~
- '*\textit{justin.g.cally@gmail.com}'
bibliography: References/SS_Extinction.bib
output:
  pdf_document: default
  html_document: default
  word_document:
    pandoc_args: --smart
header-includes: \usepackage{microtype} \usepackage[all]{hypcap} \usepackage{amsmath}
  \usepackage{booktabs} \usepackage{caption} \usepackage[labelfont=bf]{caption} \usepackage{titling}
  \pretitle{\begin{flushleft}\LARGE} \posttitle{\par\end{flushleft}\vskip 0.5em} \preauthor{\begin{flushleft}\large
  \lineskip 0.5em} \postauthor{\par\end{flushleft}} \predate{\begin{flushleft}\large}
  \postdate{\par\end{flushleft}} \usepackage{fancyhdr} \pagestyle{fancy} \fancyhead[LO,LE]{\textsl{\leftmark}}
  \rhead[]{Sexual Selection and Speciation} \usepackage[noabbrev,capitalise]{cleveref}
  \usepackage{titlefoot} \usepackage{amssymb} \usepackage{rotating} \usepackage{lineno}
  \linenumbers \usepackage{setspace}\onehalfspacing \usepackage[font={small}]{caption}
  \usepackage{epigraph} \setlength\epigraphwidth{5.25in} \setlength\epigraphrule{0pt}
  \setlength\beforeepigraphskip{1\baselineskip} \setlength\afterepigraphskip{2\baselineskip}
  \renewcommand*{\textflush}{flushright} \renewcommand*{\epigraphsize}{\footnotesize\itshape}
  \usepackage{hyperref}\hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, urlcolor=blue}
  \raggedbottom
csl: References/AmNat.csl
abstract: 'Sexual selection may influence patterns of diversification; yet controversy remains on whether sexual selection leads to a net increase or decrease in speciation rate, or even elevates extinction. Sexual selection is predicted to increase speciation rate as it can facilitate adaptation to new environments, and work alongside divergent natural selection to swiftly promote reproductive isolation. However, sexual selection frequently favours investment in costly or harmful traits that may reduce adaptation and affect diversification. Here, we investigate the association of sexual selection with speciation and extinction in passerine birds. We use two measures of sexual selection: sexual dichromatism (n = 5,812 species) and a multivariate measure of male-biased sexual selection (sexual dimorphism, polygyny and paternal care; n = 2,465), three distinct measures of speciation ($\lambda_{DR}$, $\lambda_{ND}$, $\lambda_{BAMM}$) and one measure of extinction ($\mu_{BAMM}$). Importantly, we test whether the effects of sexual selection on speciation are dependent upon ecological pressures such as temperature variability across time and space, primary productivity and range size. We find that male-biased sexual selection but not sexual dichromatism predicts speciation. Additionally, we find that birds with smaller ranges have higher speciation rates; although the direction of causality is unclear.'
---
\maketitle\unmarkedfntext{\textsuperscript{§}School of BioSciences, The University of Melbourne, Victoria, Australia.}

### 2018-10-10 Sexual Selection and Speciation.Rmd
Fix CV for BAMM

```{r, eval = F, echo = F}
MCC.BAMM.df$CV.lambda <- sqrt(exp(MCC.BAMM.df$var.lambda) - 1)*100
mean(MCC.BAMM.df$CV.lambda)
min(MCC.BAMM.df$CV.lambda)
median(MCC.BAMM.df$CV.lambda)
max(MCC.BAMM.df$CV.lambda)

#saveRDS(MCC.BAMM.df, 'data/MCC.BAMM.df.rds')

MCC.BAMM.df %>% ggplot(aes(y = CV.lambda)) +
  geom_boxplot(outlier.shape = NA)+
  scale_y_continuous(trans = "log")
```

>>>>

```{r, eval = T, echo = F, results='hide', warning=F}
MCC.BAMM.df$CV.lambda <- sqrt(exp(MCC.BAMM.df$var.lambda) - 1)*100
mean(MCC.BAMM.df$CV.lambda)
min(MCC.BAMM.df$CV.lambda)
median(MCC.BAMM.df$CV.lambda)
max(MCC.BAMM.df$CV.lambda)

saveRDS(MCC.BAMM.df, 'data/MCC.BAMM.df.rds')
# 
# MCC.BAMM.df %>% ggplot(aes(y = CV.lambda)) +
#   geom_boxplot(outlier.shape = NA)+
#   scale_y_continuous(trans = "log")
```
